Enhancing Underwater Imagery using Generative Adversarial Networks

### 2017-09-16 files/paper/tex/experiments.tex
update

We use three metrics for a quantitative evaluation. First, we compare to CycleGAN, as it inherently learns an inverse
mapping during the training of $F: X \rightarrow Y$, using the Canny edge detector
\cite{canny1986computational}. This provides a color agnostic evaluation of the images in comparison to ground truth.
Second, we compare local image patches to provide sharpness metrics on our images. Lastly, we show how an existing
tracking algorithm for an underwater robot improves performance with generated images.

@@

   ~\quad Original & ~\quad UGAN & \quad UGAN-P \\

@@

Another metric we can use to compare image patches are the mean and standard deviation of a patch. The standard
deviation gives us a sense of blurriness because it defines how far the data deviates from the mean. A lower standard
deviation means that the data is closer to the mean \starnote{not sure if we exactly need to say that because I assume the reviewers will know what it is}. In the case of images, this would suggest a blurring effect due to the data being
more clustered toward one pixel value. Table \ref{fig:mean_tbl} shows the mean and standard deviations for the local
image patches seen in Figure \ref{fig:zoom}.

@@

\begin{table}[ht]
\footnotesize
\centering
\caption{Gradient Difference Loss Metrics}
\begin{tabular}{| c | c | c | c | }
   \hline
   Patch/Method & CycleGAN & UGAN & UGAN-P \\ \hline
   Red    & 11.53 & 9.39 & 10.93  \\ \hline
   Blue   & 7.52  & 4.83 &  5.50\\ \hline
   Green  & 4.15  & 3.18 & 3.25 \\ \hline
   Orange & 6.72  & 5.65 & 5.79 \\ \hline
\end{tabular}
\label{fig:gdl_tbl}
\end{table}

\begin{table}[ht]
\footnotesize
\centering
\caption{Mean and Standard Deviation Metrics}
\begin{tabular}{| c | c | c | c | c | }
   \hline
   Patch/Method & Original & CycleGAN & UGAN & UGAN-P \\ \hline
   Red & 0.43 $\pm$ 0.23 & 0.42 $\pm$ 0.22 & 0.44 $\pm$ 0.23 & 0.45 $\pm$ 0.25 \\ \hline
   Blue & 0.51 $\pm$ 0.18 & 0.57 $\pm$ 0.17 & 0.57 $\pm$ 0.17 & 0.57 $\pm$ 0.17 \\ \hline
   Green & 0.36 $\pm$ 0.17 & 0.36 $\pm$ 0.14 & 0.37 $\pm$ 0.17 & 0.36 $\pm$ 0.17 \\ \hline
   Orange & 0.3 $\pm$ 0.15 & 0.25 $\pm$ 0.12 & 0.26 $\pm$ 0.13 & 0.27 $\pm$ 0.14 \\ \hline
\end{tabular}
\label{fig:mean_tbl}
\end{table}

>>>>

For a quantitative evaluation we compare to CycleGAN, as it inherently learns an inverse mapping during the training of
$G: Y \rightarrow X$. We first use the Canny edge detector
\cite{canny1986computational}, as this provides a color agnostic evaluation of the images in comparison to ground truth.
Second, we compare local image patches to provide sharpness metrics on our images. Lastly, we show how an existing
tracking algorithm for an underwater robot improves performance with generated images.

@@

   ~\quad Original & ~\quad \textbf{UGAN} & \quad \textbf{UGAN-P} \\

@@

Another metric we can use to compare image patches are the mean and standard deviation of a patch. The standard
deviation gives us a sense of blurriness because it defines how far the data deviates from the mean. A lower standard
deviation means that the data is closer to the mean \starnote{not sure if we exactly need to say that because I assume the reviewers will know what it is}. In the case of images, this would suggest a blurring effect due to the data being
more clustered toward one pixel value. Table \ref{fig:mean_tbl} shows the mean and standard deviations for the local
image patches seen in Figure \ref{fig:zoom}. Despite qualitative evaluation showing our methods are much sharper,
quantitatively they show only slight improvement. Other metrics such as entropy are left as future work.

@@

\begin{table}[ht]
\footnotesize
\centering
\caption{Gradient Difference Loss Metrics}
\begin{tabular}{| c | c | c | c | }
   \hline
   Patch/Method & CycleGAN & \textbf{UGAN} & \textbf{UGAN-P} \\ \hline
   Red    & 11.53 & 9.39 & 10.93  \\ \hline
   Blue   & 7.52  & 4.83 &  5.50\\ \hline
   Green  & 4.15  & 3.18 & 3.25 \\ \hline
   Orange & 6.72  & 5.65 & 5.79 \\ \hline
\end{tabular}
\label{fig:gdl_tbl}
\end{table}

\begin{table}[ht]
\footnotesize
\centering
\caption{Mean and Standard Deviation Metrics}
\begin{tabular}{| c | c | c | c | c | }
   \hline
   Patch/Method & Original & CycleGAN & \textbf{UGAN} & \textbf{UGAN-P} \\ \hline
   Red & 0.43 $\pm$ 0.23 & 0.42 $\pm$ 0.22 & 0.44 $\pm$ 0.23 & 0.45 $\pm$ 0.25 \\ \hline
   Blue & 0.51 $\pm$ 0.18 & 0.57 $\pm$ 0.17 & 0.57 $\pm$ 0.17 & 0.57 $\pm$ 0.17 \\ \hline
   Green & 0.36 $\pm$ 0.17 & 0.36 $\pm$ 0.14 & 0.37 $\pm$ 0.17 & 0.36 $\pm$ 0.17 \\ \hline
   Orange & 0.3 $\pm$ 0.15 & 0.25 $\pm$ 0.12 & 0.26 $\pm$ 0.13 & 0.27 $\pm$ 0.14 \\ \hline
\end{tabular}
\label{fig:mean_tbl}
\end{table}
